Preliminary Draft

### 2021-07-21 article/draft.tex
typo

Section $230$ in the United States Communications Decency Act provides immunity for website platforms against the content created by users. Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for Mainstream Social Media Platforms, such as Facebook, Twitter or YouTube, to moderate the available content. In particular, platforms take explicit actions when content is in violation of local laws in different jurisdictions, such as laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws. For example, Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}. We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} %Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned YouTube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}). Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged, suspending accounts, implementing strike systems, reducing the visibility of content, etc. As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines (as of July 2021). The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''. Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).

>>>>

Section $230$ in the United States Communications Decency Act provides immunity for website platforms against the content created by users. Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for mainstream social media platforms, such as Facebook, Twitter or YouTube, to moderate the available content. In particular, platforms take explicit actions when content is in violation of local laws in different jurisdictions, such as laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws. For example, Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}. We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} %Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned YouTube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}

@@

During the COVID-19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}). Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged, suspending accounts, implementing strike systems, reducing the visibility of content, etc. As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines (as of July 2021). The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''. Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).
